Numerical simulation of the Cordilleran ice sheet through the last glacial cycle

### 2014-05-27 cordillera-cycle.tex
Add LGM figure into manuscript.

@@

>>>>

The modelled last glacial maximum ice sheet possess a central divide located at
about 3\,500\,\unit{m} elevation along the spine of the Rocky Mountains. The
distribution of surface velocites shows a clear assymetry between the maritime,
western flank, and the continental, eastern flank of the ice sheet
(Fig.~\ref{fig:lgm}).

@@

% fig:lgm
\begin{figure}
  \includegraphics{lgm}
  \caption{Modelled ice surface topography (100\,\unit{m} contours) and
           velocity (\unit{m\,yr^{-1}}) corresponding to the last glacial
           volume maximum.}
  \label{fig:lgm}
\end{figure}
